---
title: "Package Tutorial"
author: "Tanner Bahm"
date: "`r Sys.Date()`"
output: html_document
---

# An Introduction to My R Package
### smol
My R package is *super* cool and it does *__three__* things.
new line!!!! except it doesn't 

need a space between to get new paragraph

embed R code use three tick marks and curly brace

```{r}
sum(1,2)
```

## Installation Instructions

You will need to download data to use this package. Here is the code you can use to do this. 
```{r echo=TRUE}
download.file("https://raw.githubusercontent.com/tannerbahm/bahm_pkg/master/data/surveys.csv", destfile = "/cloud/project/data/surveys.csv")
```

```{r eval=FALSE, include=TRUE}
install.packages("phytools")
```


text can be included anywhere in doc, there is no limit!
but... text in a code chunk must be commented (# before text)

```{r}
sum(1,2)
# like dis
```

to embed images
![Caption](path/to/image)

has to be uploaded to R first

can't use JPEG

it's also possible to inlcude [hyperlinks](website.url)
