---
title: "Package Tutorial"
author: "Tanner Bahm"
date: "`r Sys.Date()`"
output: html_document
---

# An Introduction to My R Package

My R package contains three different functions and can be used for data cleaning purposes, data visualization via box plot, and statistical analysis using a linear model. 

## Download the Package

```{r, eval=FALSE}
remotes::install_gitgub("tannerbahm/bahm_pkg")
library(argh)
```

## Installation Instructions

You will need to download data to use this package. Here is the code you can use to do this. 
```{r, eval=FALSE}
download.file("https://raw.githubusercontent.com/tannerbahm/bahm_pkg/master/data/surveys.csv", destfile = "/cloud/project/data/surveys.csv")
```

You will need to download tidyverse to use this package. Here is the code if you do not already have tidyverse.

```{r eval=FALSE}
install.packages("tidyverse")
library(tidyverse)
```

## Examples of the Functions Included

First, we will want to remove any NA values in the data set. We will use this function to do so:

clean_data <- function(filepath){
  raw_data <- read_csv(filepath)
  data_clean <- raw_data %>% 
    na.omit()
ma  if (sum(is.na(data_clean)) == 0)
    return(data_clean)
  else{
    print("nas present :(")
  }
}

We'll save the surveys data set to a variable.

```{r, eval=FALSE}
surveys <- read_csv("/cloud/project/data/surveys.csv")
```

Now we will remove the NA values and save that to a variable as well. 

```{r, eval=FALSE}
surveys_clean <- clean_data("/cloud/project/data/surveys.csv")
```

You can view the clean data by using this code:
```{r, eval=FALSE}
View(surveys_clean)
```

Next, we will use the box plot function to visualize the data. This is the function we will use:

make_boxplot <- function(filepath){
  boxplot_data <- read_csv(filepath)
  make_plot <- boxplot_data
  boxplot <- ggplot(data = make_plot, mapping = aes(x = species_id, y = weight)) + geom_boxplot()
  return(boxplot)
}

We'll use the file path to the surveys data set.

```{r, eval=FALSE}
make_boxplot("/cloud/project/data/surveys.csv")
```

The last function in my R package is a linear model summary. This is the function:

lin_model <- function(filepath){
  lin_data_raw <- read_csv(filepath)
  lin_data <- lin_data_raw
  model_fit <- lm(hindfoot_length ~ weight, data = lin_data)
  return(summary(model_fit))
}

Once again, we'll use the file path to the data set.

```{r, eval=FALSE}
lin_model("/cloud/project/data/surveys.csv")
```

